The Cluster Difference Imaging Photometric Survey (CDIPS). I. Method \& TESS Light Curves from Sector 6

### 2019-05-13 paper/ms.tex
paper: wrote some words

\title{
  The Cluster Difference Imaging Photometric Survey (CDIPS).
  I. Method \& TESS Light Curves from XXX Clusters
}

@@

In what follows, \S~\ref{sec:method} presents BLAH, and
\S~\ref{sec:results} describes BLAH BLAH.
\S~\ref{sec:discussion} discusses, and \S~\ref{sec:conclusion}
concludes.

@@

\citet{rizzuto_multidimensional_2011} also focused on a single moving
group: the Sco OB2 association. We used their reported Hipparcos
identifiers, and matched against the {\it Gaia} archive's
\texttt{hipparcos2_best_neighbour} table, which gave 319
nearest-neigbor stars from 436 candidate members.

Finally, \citet{oh_comoving_2017} searched for comoving stars in the
$\approx$2 million stars that overlapped between Tycho-2 and {\it
Gaia}-DR1.  They found many wide binaries, and also identified a large
number of comoving groups.  We chose the 2{,}134 stars that they
reported were in groups with sizes of at least 3 stars.  Using their
{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
archive's \texttt{dr1_neighbourhood} table, which gave 1{,}881
nearest-neigbor stars in groups of at least three stars
\citep{marrese_gaia_2019}.

@@

After collecting the results of all the studies described above, we
merged them into a single table. We queried the
\texttt{gaiadr2.gaia_source} table to retrieve their photometric $G$,
$G_{\rm R_p}$, and $G_{\rm B_p}$ magnitudes, as well as their
five astrometric parameters $(\alpha, \delta, \mu_\alpha, \mu_\delta,
\pi)$.
We then imposed that $G_{\rm R_p} < 16$.
The concatenated results are given in Table~N.

@@

>>>>

\title{
  The Cluster Difference Imaging Photometric Survey (CDIPS).
  I. Method \& TESS Light Curves from Sector 6
}

@@

The exoplanet field is evolving.
At the beginning, Doppler spectroscopy by the Geneva and California groups
led to the first exoplanet detections (CITE: Mayor 95, Butler, Marcy).
Some of these planets transited (CITE: Henry, Charbonneau).
Despite the geometric rarity of transits, photometric monitoring can
be performed in parallel, while spectroscopy cannot.
This enabled thousands of planet detections with the Kepler spacecraft
(CITE: Borucki, Morton).
The abundance of planets from Kepler taught us about statistics
(CITE: Howard, Fressin, Petigura).
By nature of its design, Kepler left open two major avenues for
improvement: (i) brighter stars, (ii) rare weirdos.
TESS (CITE: Ricker), by nature of its small, wide-field cameras, and
nearly all-sky coverage, can capitalize on both.
TESS observes more stars than Kepler, for on average less time.
One class of rare weirdo to which TESS is sensitive is stars in
clusters.  For brevity, we use the term ``cluster'' to refer to open
clusters, moving groups, associations, and star-forming regions.
Each of the $\sim$1000 star clusters of the Milky Way is a gift to
astrophysics, providing a sample of stars that vary widely in mass
but all have approximately the same age and composition.

Cluster stars have been monitored photometrically from the ground
(CITE: Joel thesis, Cambridge group).
A few clusters, NAME1 and NAME2, were observed by Kepler in its prime
mission (CITE: Meibom).
And a few more, most notably including X,Y,Z, were observed in K2's
ecliptic mission (CITE).

TESS holds the promise to deliver the most homogeneous and
comprehensive cluster photometric survey in history.  Based on the
cluster membership database of \citet{Kharchenko_et_al_2013} and the
TESS apparent magnitude calculator of \citet{Jaffe_Barclay_2017}, we
estimate that $10^5$ cluster members brighter than $T=16$ will be
observed in the northern ecliptic hemisphere's full-frame images.

Yet, there are formidable obstacles to deriving precise photometry
from the {\it TESS} images because of the relatively poor angular
resolution.  Almost all of the clusters are within 10 degrees of the
Galactic plane (see Figure~1), where the problems with crowding and
complex backgrounds are so severe that the {\it TESS}\, Science Team
has neglected that portion of the sky in their planet simulations
\citep{Sullivan_et_al_2015}. Similarly, the {\it TESS}\, Candidate
Target List deprioritizes all objects within $15^\circ$ of the
galactic plane~\citep{stassun_TIC_2018}, which includes 90\% of all
star clusters.  The large pixel size and the high stellar surface
density will make aperture photometry unreliable.  Yet, aperture
photometry is the basis of the official {\it TESS} data reduction
pipeline and almost all reduction methods that have been applied to
{\it Kepler} and {\it K2} data.

We have begun to produce photometry from the TESS images.
In what follows, \S~\ref{sec:method} presents BLAH, and
\S~\ref{sec:results} describes BLAH BLAH.
\S~\ref{sec:discussion} discusses, and \S~\ref{sec:conclusion}
concludes.

@@

\citet{rizzuto_multidimensional_2011} also focused on a single moving
group: the Sco OB2 association. We used their reported Hipparcos
identifiers, and matched against the {\it Gaia} archive's
\texttt{hipparcos2\_best\_neighbour} table, which gave 319
nearest-neigbor stars from 436 candidate members.

Finally, \citet{oh_comoving_2017} searched for comoving stars in the
$\approx$2 million stars that overlapped between Tycho-2 and {\it
Gaia}-DR1.  They found many wide binaries, and also identified a large
number of comoving groups.  We chose the 2{,}134 stars that they
reported were in groups with sizes of at least 3 stars.  Using their
{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
nearest-neigbor stars in groups of at least three stars
\citep{marrese_gaia_2019}.

@@

After collecting the results of all the studies described above, we
merged them into a single table. We queried the
\texttt{gaiadr2.gaia\_source} table to retrieve their photometric $G$,
$G_{\rm R_p}$, and $G_{\rm B_p}$ magnitudes, as well as their
five astrometric parameters $(\alpha, \delta, \mu_\alpha, \mu_\delta,
\pi)$.
We then imposed that $G_{\rm R_p} < 16$.
The concatenated results are given in Table~N.

@@

During the period search, we rejected $6\,{\rm hours}$ at the
beginning and end of each spacecraft orbit, to mitigate the presence
of correlated red noise in the results.
This shrinks the data volume by about 5\%, but also lowers the number
of systematic false positives in subsequent vetting.
